---
title: "Assignment 2"
author: "Victor Asum"
date: "2024-11-21"
output: word_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

**Is the perception of media freedom associated with citizens' satisfaction with democracy in Ghana?**

*Explainatory Variable*: Perception of Media Freedom (Q33H)

*Response Variable*: Satisfaction of democracy (Q31)


**Does primary langauge used in interview influence the length of the interview?**

*Explanatory Variable*:  Language of interview (Q102)

*Response Variable*: Length of interview (LENGTH)


# SECTION 1:
```{r}
library(descr)
library(haven)
GH_AFRO_9 <- read_sav("C:/Users/AiAsum/Downloads/afrobarometer_release-dataset_gha_r9_en_2023-04-01.sav")

```


# Section 2: 
Sub
```{r}
vars <- c("Q33H", "Q31", "Q102", "LENGTH") 
cleanData <- GH_AFRO_9[vars]
save(cleanData, file='PA2_Research.RDATA')

```


# Section 2 b: Error handling and Labeling variable response categories

```{r}

# first research questions

# Perception of Media Freedom (Q33H)
cleanData$Q33H <- as.character(cleanData$Q33H)

cleanData$Q33H[cleanData$Q33H == "8"] <- NA
cleanData$Q33H[cleanData$Q33H == "9"] <- NA
cleanData$Q33H[cleanData$Q33H == "-1"] <- NA


# Satisfaction of democracy (Q31)
cleanData$Q31 <- as.character(cleanData$Q31)
cleanData$Q31[cleanData$Q31 == "8"] <- NA
cleanData$Q31[cleanData$Q31 == "9"] <- NA
cleanData$Q31[cleanData$Q31 == "-1"] <- NA



# Second research question
# Language of interview (Q102)
cleanData$Q102 <- as.character(cleanData$Q102)


summary(cleanData$LENGTH)
mean(cleanData$LENGTH, na.rm = TRUE)
sd(cleanData$LENGTH, na.rm = TRUE)




freq(cleanData$Q33H, cex.names=0.5, ylab = "Frequency", xlab = "Citizen's Perceive of Media freedom")
freq(cleanData$Q31, cex.names=0.5, ylab = "Frequency", xlab = "Citizen's Satisfaction of Democracy")

freq(cleanData$Q102, cex.names=0.5, ylab = "Frequency", xlab = "Language used in interview")
hist(cleanData$LENGTH, main="Histogram of interview length", xlab="interview length (minutes)", ylab="Frequency", col="#ff00ff")



```


# Section 3 - 
```{r}
# I'm Creating secondary variables for media and democracy
# I choose to combine Not at all free", "Not very free", as one,"Somewhat free", "Completely free"
cleanData$Q33H[cleanData$Q33H == "0"] <- "1"

# I choose to combine Not at all free", "Not very free", as one,"Somewhat free", "Completely free"
cleanData$Q31[cleanData$Q31 == "0"] <- "1"


# Second Research:
# Primary Language used for the research
cleanData$Q102 <- as.character(cleanData$Q102)
cleanData$Q102[cleanData$Q102 == "261"] <- "9995"
cleanData$Q102[cleanData$Q102 == "262"] <- "9995"
cleanData$Q102[cleanData$Q102 == "263"] <- "9995"
cleanData$Q102[cleanData$Q102 == "264"] <- "9995"


# Changing to understanable variables
 cleanData$Q33H <- factor(cleanData$Q33H,
                          levels = c("1", "2", "3"),
                          labels = c("Not free", "Somewhat free", "Completely free")
                          )

 cleanData$Q31 <- factor(cleanData$Q31,
                        levels = c("1", "2", "3", "4"),
                        labels = c("Not at all satisfied", 
                                    "Not very satisfied", "Fairly satisfied", 
                                    "Very satisfied"))
 
cleanData$Q102 <- factor(cleanData$Q102,
                          levels = c("1", "260", "9995"),
                          labels = c("English", "Twi", "Others"))

freq(cleanData$Q33H, cex.names=0.5, ylab = "Frequency", xlab = "Citizen's Perceive of Media freedom")
freq(cleanData$Q31, cex.names=0.5, ylab = "Frequency", xlab = "Citizen's Satisfaction of Democracy")

freq(cleanData$Q102, cex.names=0.5, ylab = "Frequency", xlab = "Language used in interview")
hist(cleanData$LENGTH, main = "Histogram of interview length", xlab = "interview length (minutes)")



```


# Section 4

```{r}
# First Research

mediaTable <- table(cleanData$Q31, cleanData$Q33H)
mediaTable_colProp <-prop.table(mediaTable, 2)
round(mediaTable_colProp, 3)


# Second research
tapply(cleanData$LENGTH, cleanData$Q102, mean, na.rm = TRUE)
tapply(cleanData$LENGTH, cleanData$Q102, sd, na.rm = TRUE) 
tapply(cleanData$LENGTH, cleanData$Q102, length)




```

# SECTION 4:
```{r}
colors1 <- c("#AA5486", "#47663B", "#E8ECD7", "#EED3B1")
colors2 <- c("#181C14", "#FC8F54", "#697565","#AA5486")

barplot(
  mediaTable_colProp, 
  beside = TRUE,                
  cex.names = 0.6,
  ylim = c(0, 0.5),
  col = colors2,  
  xlab = "Perception of Media Freedom", 
  ylab = "Proportion of Citizen"
)

legend(
  "top",   
  legend = rownames(mediaTable_colProp),
  fill = colors2,
  title = "Level Satisifaction",
  cex = 0.6
)


# Box and whiaker plot
boxplot(cleanData$LENGTH ~ factor(cleanData$Q102),
        names = levels(factor(cleanData$Q102)),
        main = "Distribution of Length of interview for each primary langauge",
        xlab = "Primary language",
        ylab = "Length",
        ylim = c(0, max(cleanData$LENGTH, na.rm = TRUE) + 10),
        col = "lightblue"
)


```

## Summary 
 to have the perception that that all civil servant are corruption compare to other living condition. 



